Verifying Demonstrations

### 2020-07-05 paper/intro.tex
Makes related work a part of the intro
makes scenario location-relevant, fixes language in intro

Although there are numerous contributions in the field of \ac{DB} 
authentication protocols, the majority of them are shared-key protocols.
This means that the prover and the verifier must share a secret.
This might work for key-less entry protocols for cars, where the car and keyfob 
can share a key.
But it does not work for ubiquitous \ac{DB} authentication.

Our work present contributions in the area of \ac{DB} public-key protocols, 
particularly \ac{DB} \acp{ZKPK}.
This allows anyone to act as a verifier, unlike in the shared-key scenario 
where the verifier must be trusted.
The \ac{ZK} property also enables a variety of privacy properties, such as 
anonymity.

>>>>

Although there are numerous contributions in the field of \ac{DB} 
authentication protocols, the majority of them are shared-key protocols.
This means that the prover and the verifier must share a secret.
This works for scenarios like key-less entry protocols for cars, where the car and keyfob 
can share a key.
It does, however, not work for ubiquitous \ac{DB} authentication where
the prover and verifier may not have met before.

Our work present contributions in the area of \ac{DB} public-key protocols, 
particularly \ac{DB} \acp{ZKPK}.
This allows anyone to act as a verifier, unlike in the shared-key scenario 
where the verifier must be trusted.
The \ac{ZK} property also enables a variety of privacy properties, such as 
anonymity.
With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is close to a specific car, has a valid driver's license, is older than 18 
(without revealing her actual age), has the relevant car-sharing subscription which is not 
\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
and  Bob can be sure that Alice is not just relaying messages 
from her older sister Carol or \ac{DBMF} relaying the subscription from some 
unsuspecting stranger also waiting in the parking lot.
